---
title: "Ballis's Benchmark Analysis"
author: Larry Tentor
output:
  html_document:
    df_print: paged
---


```{r configuration, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(width = 80)
library(data.table)
library(ggplot2)
library(plyr)
library(dplyr)
library(sqldf)
#library(xlsx)
```


## Analysis Setup
```{r setup}
pathData <- "C:\\Users\\Larry\\Dropbox\\Family\\LBTentor\\Professional\\Teaching\\Decision Analytics\\Analytics Formulation\\Fall 2018\\Session 02\\Ballis Benchmark\\"
```

## Analysis Load Data
### Head of data frame
```{r Load}
#fundData <- read.xlsx(paste0(pathData,"Ballis Benchmark A F-1621X.xlsx"), sheetName = "Downloaded Data")
rowsToLoad <- Inf
fundData   <- fread(paste0(pathData,"MorningstarData.txt"),sep="\t",nrows=rowsToLoad,header=TRUE)
head(fundData[,1:4])
```

### Tail of data frame
```{r}
tail(fundData[,1:4])
```

### Field Names
```{r}
options(width=92)
names(fundData)
```

## Analysis: Determine Counts

### Count By Benchmark
```{r}
# Alternatives
fundData$Benchmark <- factor(fundData$"Primary Prospectus Benchmark")
Benchmark          <- fundData$"Primary Prospectus Benchmark"
Size               <- fundData$"Fund Size"
fundData2          <- data.frame(Benchmark)
countBenchmark01   <- count(fundData2, Benchmark)
countBenchmark02   <- aggregate(fundData2, by = list(Benchmark), FUN = length)

# Simpliest
countBenchmark     <- aggregate(fundData$"Primary Prospectus Benchmark", by = list(fundData$"Primary Prospectus Benchmark"), FUN = length)
countBenchmark     <- countBenchmark[order(-countBenchmark$x),]
head(countBenchmark,10)

```
### Count By Global Category
```{r}
countGlobalCategory     <- aggregate(fundData$"Global Category", by = list(fundData$"Global Category"), FUN = length)
countGlobalCategory     <- countGlobalCategory[order(-countGlobalCategory$x),]
head(countGlobalCategory,10)
```

### Count By Global Category
```{r}
countMorningstarCategory     <- aggregate(fundData$"Morningstar Category", by = list(fundData$"Morningstar Category"), FUN = length)
countMorningstarCategory     <- countMorningstarCategory[order(-countMorningstarCategory$x),]
head(countMorningstarCategory,10)
```

## Subset Data
```{r}
keepSP     <- fundData$`Primary Prospectus Benchmark` =='S&P 500 TR' 
keep2000   <- !is.na(fundData$`Yearly Return 2000`)
keep       <- keepSP & keep2000
fundDataSP <- fundData[keep,]
message('        Starting Number of Funds: ', nrow(fundData))
message('     Number of SP 500 Benchmarks: ',sum(keepSP))
message('Number of Funds with 2000 Return: ',sum(keep2000))
message('        Number of Analysis Funds: ',sum(keep))
message('       Number of funds remaining: ',nrow(fundDataSP))
head(fundDataSP[,c(1:3,12,32)])
tail(fundDataSP[,c(1:3,12,32)])
```
## Calculate Bucket Returns
```{r}
fundDataSP$ReturnBucket01 <- ((1+fundDataSP$`Yearly Return 2000`/100)*(1+fundDataSP$`Yearly Return 2001`/100)*(1+fundDataSP$`Yearly Return 2002`/100)*(1+fundDataSP$`Yearly Return 2003`/100)*(1+fundDataSP$`Yearly Return 2004`/100)-1)*100
fundDataSP$ReturnBucket02 <- ((1+fundDataSP$`Yearly Return 2005`/100)*(1+fundDataSP$`Yearly Return 2006`/100)*(1+fundDataSP$`Yearly Return 2007`/100)*(1+fundDataSP$`Yearly Return 2008`/100)*(1+fundDataSP$`Yearly Return 2009`/100)-1)*100
fundDataSP$Quartile01 <- ntile(fundDataSP$ReturnBucket01, 4) 
fundDataSP$Quartile02 <- ntile(fundDataSP$ReturnBucket02, 4) 

head(fundDataSP[,c('Name','ReturnBucket01','ReturnBucket02','Quartile01','Quartile02')])
```

### Transistion Matrix
```{r}
countQuartileTransition     <- aggregate(fundDataSP$Name, by = list(fundDataSP$Quartile01,fundDataSP$Quartile02), FUN = length)
countQuartileTransition
transitionMat <- matrix(, nrow = 4, ncol = 4)
for(row in 1:16){
  transitionMat[countQuartileTransition$Group.1[row], countQuartileTransition$Group.2[row]] <- countQuartileTransition$x[row]
}
#transitionMat[countQuartileTransition$Group.1,countQuartileTransition$Group.2] <- countQuartileTransition$x  
transitionMat
transitionMat/sum(transitionMat)
```
## Calculate Fund Flow
```{r}
fundDataSP$FundFlow01 <- (fundDataSP$`Fund Size 2001-12`-fundDataSP$`Fund Size 2000-12`*(1+fundDataSP$`Yearly Return 2000`/100))/fundDataSP$`Fund Size 2000-12`
fundDataSP$FundFlow02 <- (fundDataSP$`Fund Size 2002-12`-fundDataSP$`Fund Size 2001-12`*(1+fundDataSP$`Yearly Return 2000`/100))/fundDataSP$`Fund Size 2001-12`
fundDataSP$FundFlow03 <- (fundDataSP$`Fund Size 2003-12`-fundDataSP$`Fund Size 2002-12`*(1+fundDataSP$`Yearly Return 2000`/100))/fundDataSP$`Fund Size 2002-12`
fundDataSP$FundFlow04 <- (fundDataSP$`Fund Size 2004-12`-fundDataSP$`Fund Size 2003-12`*(1+fundDataSP$`Yearly Return 2000`/100))/fundDataSP$`Fund Size 2003-12`
fundDataSP$FundFlow05 <- (fundDataSP$`Fund Size 2005-12`-fundDataSP$`Fund Size 2004-12`*(1+fundDataSP$`Yearly Return 2000`/100))/fundDataSP$`Fund Size 2004-12`
fundDataSP$FundFlow06 <- (fundDataSP$`Fund Size 2006-12`-fundDataSP$`Fund Size 2005-12`*(1+fundDataSP$`Yearly Return 2000`/100))/fundDataSP$`Fund Size 2005-12`
fundDataSP$FundFlow07 <- (fundDataSP$`Fund Size 2007-12`-fundDataSP$`Fund Size 2006-12`*(1+fundDataSP$`Yearly Return 2000`/100))/fundDataSP$`Fund Size 2006-12`
fundDataSP$FundFlow08 <- (fundDataSP$`Fund Size 2008-12`-fundDataSP$`Fund Size 2007-12`*(1+fundDataSP$`Yearly Return 2000`/100))/fundDataSP$`Fund Size 2007-12`
fundDataSP$FundFlow09 <- (fundDataSP$`Fund Size 2009-12`-fundDataSP$`Fund Size 2008-12`*(1+fundDataSP$`Yearly Return 2000`/100))/fundDataSP$`Fund Size 2008-12`

fundDataSP$Growth05 <- ifelse(fundDataSP$FundFlow05>median(fundDataSP$FundFlow05, na.rm=TRUE),1,-1)
fundDataSP$Growth05[is.na(fundDataSP$Growth05)] <- 0
head(fundDataSP[,c('Name','ReturnBucket01','ReturnBucket02','Quartile01','Quartile02','FundFlow05','Growth05')])
```

### Transistion Matrix
```{r}
countQuartileTransitionByGrowth     <- aggregate(fundDataSP$Name, by = list(fundDataSP$Quartile01,fundDataSP$Quartile02,fundDataSP$Growth05), FUN = length)
countQuartileTransitionByGrowth$Group.3 <- countQuartileTransitionByGrowth$Group.3+2
countQuartileTransitionByGrowth
```

```{r}
transitionMatGrowth <- array(0, dim=c(4,4,3))
for(row in 1:nrow(countQuartileTransitionByGrowth)){
  transitionMatGrowth[countQuartileTransitionByGrowth$Group.1[row], countQuartileTransitionByGrowth$Group.2[row], countQuartileTransitionByGrowth$Group.3[row]] <- countQuartileTransitionByGrowth$x[row]
  
  #message(paste0('['
  #               ,countQuartileTransitionByGrowth$Group.1[row],','
  #               ,countQuartileTransitionByGrowth$Group.2[row],','
  #               ,countQuartileTransitionByGrowth$Group.3[row],'] = '
  #               ,countQuartileTransitionByGrowth$x[row]))
}
transitionMatGrowth[,,1]
```

```{r}
transitionMatGrowth[,,2]
```

```{r}
transitionMatGrowth[,,3]

```

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
